NURM: a tool to locate numerical differences in pipelines

### 2019-06-14 paper.tex
Edit Fig1 and revise corresponding text

Figure~\ref{fig:overview} shows an overview of our method. For each tested
condition, Condition 1 and Condition 2, the pipeline is containerized with
Docker, and its interface is described with
Boutiques~\cite{glatard2017boutiques}. \reprozip~\cite{Chirigati2016} is
added to Condition 1 for provenance tracking. Our tool starts by
identifying temporary files and ``multi-write" files, i.e., files written
by more than one process (Fig.~\ref{fig:overview-capturing}) \tristan{check if concurrent writes are discussed}. To do that,
the tool first executes the pipeline in Condition 1, to obtain a process
graph (Fig.~\ref{fig:overview-capturing} - (P)) and a list of result files.
The list of processes that create intermediary or multi-write
files is then generated. Using this list, the tool modifies Docker image in Condition 1 and
exectutes the pipeline again through it, which turns to produce results
including temporary and overwritten files
(Fig.~\ref{fig:overview-capturing} - (C1)). In the second step, the
processes are labeled from the differences found in their outputs in the
two tested conditions (Fig.~\ref{fig:overview-labelling}). To this order,
the tool builds docker image for Condition 2 by modifying pipeline
processes that recognised from the process graph. Then, the modified docker
image is executed in Condition 2 and each process is labeled right after
the running by comparing checksum of the results obtained in Condition 1
and output files of the process in Condition 2
(Fig.~\ref{fig:overview-labelling} - (D)). We then label processes in 2
categories (Fig.~\ref{fig:overview-labelling} - (L)) depending whether they
create differences (represented in red) or not (green). Process labelling
is done through hooks which are defined during the docker image modifying
procedure, and incremental updates in Condition 2, until the end of the
pipeline execution.

\tristan{Fig 1-a isn't in the git repo while I had asked it before and it is 
written in the getting started guide anyway. It is annoying to have to ask for these things
multiple times while I would like to focus on the content. Also, ppt is among the worst formats
to put in a git repo as it doesn't play well with diffs.}

\tristan{In Fig 1-a, change ``overwritten'' to ``multi-write''.}

\tristan{We should also discuss the cardinality of ``input subject''. Are we talking
about 1 subject or all subjects?}

\begin{figure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \includegraphics[width=1\columnwidth]{images/Slide2}
    \caption{Identification of temporary and multi-write files.}
    \label{fig:overview-capturing}
  \end{subfigure}
   \begin{subfigure}{\columnwidth}
    \centering
     \includegraphics[width=1\columnwidth]{images/Slide1}
     \caption{Process labelling.}
     \label{fig:overview-labelling}
   \end{subfigure}
   \caption{Method overview}
   \label{fig:overview}
  \end{figure}

@@

We use \reprozip (Fig.~\ref{fig:overview-capturing} - (P))
to capture: (1) the set of processes created by the
pipeline, using the \texttt{clone()} or \texttt{fork()} system call, and
(2) the set of files read, written and executed by each process, including
temporary files. \reprozip collects this information through the
\texttt{ptrace()} system call and stores it in a SQLite database.

Our tool reconstructs a process tree starting from the first process
created by the pipeline and traversing processes through \texttt{clone()}
and \texttt{fork()} dependencies. Our tool also creates a process \emph{graph} from this tree
by adding edges corresponding to file dependencies between processes. A
file dependency is defined between processes A and B if a file written by A
is read by B. Figure~\ref{fig:simple_script} shows an example of a process
tree and graph constructed from the example pipeline in
Listing~\ref{listing:sample-script}.
\begin{listing}
\begin{minted}[frame=single,
  framesep=3mm,
  linenos=false,
  xleftmargin=0pt,
  tabsize=4]{bash}
#!/bin/bash

@@

\tristan{You should use Fig. or Figure consistently}

@@

The label of processes that read or 
write temporary files is undetermined because these files are deleted during 
the execution. To address this issue, we replace in Condition 1 every process P that 
writes temporary files with a modification of P that first calls P and then
saves all its output files to a read-only directory. This replacement is
done by modifying the PATH environment variable to point to a directory
containing a modified version of the executable called by the process. The
modified executable will run the original executable and then save its
output files (see Listing~\ref{listing:modify-script}). 
\tristan{Add more comments, in particular to explain what the variables represent.}
This 
solution does not cover the temporary files that are removed by P 
itself, but this is not a problem since these files do not play any role in 
the subsequent steps of the pipeline. 
\begin{listing}
  \begin{minted}[frame=single,
    framesep=3mm,
    linenos=false,
    xleftmargin=0pt,
    tabsize=4]{python}
  #!/usr/bin/env python
  import os.path as op

  # Execute process in cond2 from backup folder
  p_name = sys.argv[0]
  p_exec_cond2 = op.join('backup_scripts', p_name)
  p_exec_cond2 = p_exec_cond2 + " ".join(sys.argv[1:])
  subprocess.Popen(p_exec_cond2, shell=True).communicate()

  # Load list of process to be checked
  with open('path/to/p_list/', 'r') as p_list:
      process_list = json.load(p_list)

  if p_exec_cond1 in process_list.keys():
      # Make backup copy
      capture_file(p_files, from_cond1, to_backup)

  \end{minted}
    \caption{Modified version of the script in Listing~\ref{listing:sample-script} to save temporary files.}
    \label{listing:modify-script}
  \end{listing}

\subsubsection{Capturing multiple write files}

@@

For example, in the sample pipeline in 
Listing~\ref{listing:sample-script}, process \texttt{2\#bet2} write a temporary file and 
also file \emph{T1w\_brain\_bin.nii.gz} is first written by process \texttt{2\#bet2} and 
then overwritten by process \texttt{3\#fslmaths}. The list of these processes are captured in 
Listing~\ref{listing:json_process}.
Using this list, we modify relevant processes in Condition 1 and then re-execute pipeline 
to store them in a backup folder.
Figure~\ref{fig:overview-capturing} - (C1) shows pipeline results including intermediary files 
captured as the outputs in Condition 1.

@@

Since all the result files are captured in Condition 1, the tool 
is ready to label the piepeline processes based on the results in Condition 2.
However, another challenge is to label undetermined processes that read files with 
differences and write files with differences too. In such 
situations, it is not possible to determine from the pipeline results 
whether the process created differences, removed some differences, or 
was transparent.
To address this issue, we set hooks in the pipeline 
in Condition 2. Hooks are set by replacing the pipeline 
processes with a custom script. This custom script labels each process 
as \emph{transparent} or \emph{create differences} immediately after running 
the original executable. 
The replacement is done through the PATH variable, as before. Moreover, 
this custom script copies the results obtained from the same process in 
Condition 1 to the pipeline output in Condition 2 if 
it is invoked with 
the arguments of a process that created differences. 
Differences are identified by comparing checksum of the output files for 
the same process in both conditions.
We developed an incremental approach that consists of the following steps:

\begin{enumerate}
  \item Start the pipeline execution in Condition 2; 
        after hooking all the processes involved in the pipeline.
  \item Label each process as \emph{transparent} or \emph{create differences} 
        right after its running (Fig.~\ref{fig:overview-labelling} - (L)).
  \item Check if process is \emph{create differences} then: 
        copies the results produced by the same process in Condition 1 to the 
        pipeline output in Condition 2 (Fig.~\ref{fig:overview-labelling} - (M)). 
  \item Continue steps 2 and 3 until the end of the pipeline execution.
\end{enumerate}

This algorithm create a labeled process graph at the end of pipeline execution 
(Fig.~\ref{fig:overview-labelling} - (LG)).

@@

Figure~\ref{fig:iterations} illustrates our incremental labelling 
process for the example in Figure~\ref{fig:simple_script}. At every 
step, processes that created differences are shown in red and other processes 
(transparent processes) are in green. As in 
Figure~\ref{fig:simple_script}, plain black edges represent the process 
tree and dashed edges represent file dependencies: green edges 
represent files with no differences, while red edges represent files with 
differences. Temporary files are not represented because they have been 
backed up as previously described.

The four steps in Figure~\ref{fig:iterations} correspond to the 
steps of the labelling algorithm. 
At step one, process \texttt{1\#bet} is executed and then labeled 
as transparent (green) as it produced files without differences.
At step 2, \texttt{2\#bet2} 
is labeled as difference creator (red) as it produced files with differences 
from files without differences. Therefore, the files produced by \texttt{2\#bet2} in  
Condition 2 are replaced with the files produced by \texttt{2\#bet2} in 
Condition 1.
At step 3, after running process \texttt{3\#fslstats}, it labeled as 
transparent as it write files without differences.
At step 4, process \texttt{4\#fslmaths} is labeled as difference creator 
as the last process of the pipeline.
As a result of these 4 steps, the final process labelling is: 
\texttt{2\#bet2} and \texttt{4\#fslmath} are difference creators (red) 
and the other processes are transparent.
It should be noted that processes that remove differrences are not recognised 
by this method.

@@

Different subjects may lead to different process trees and graphs, due to
variations that may be coming from differences in data types or
cardinality. For instance, some images may have been acquired multiple
times in some subjects. Some of these differences can be neglected, for
instance when a data decompression step is present at the beginning of the
execution for some subjects only, and other ones cannot, when different
processing paths are used in different subjects.

To address this issue, we use the tree edit distance~\cite{zhang1989simple}
to measure the distance between labeled trees \tristan{how about graphs?
also, why between \emph{labeled} trees and not just trees?}, defined as the
minimum weighted \tristan{weighted by what?} number of edit operations
required to transform one tree into the other one. Three edit operations
are considered: node label modification, node removal, and node insertion.
Each operation has an associated cost: 1 for insertion and removal, and
either 1 or 2 for label modification depending on the type of modification. \tristan{Please check my edits.}

With this distance, we cluster subjects using agglomerative hierarchical
clustering as implemented in SciPy~\cite{oliphant2007scipy}
(Algorithm~\ref{algo:hclustering}). As a result, the distance between
any two subjects in a cluster is lower than a threshold parameter.

@@

\tristan{how do you choose the representative process graph in each cluster?}

@@

The Human Connectome Project (\href{https://www.humanconnectome.org}{HCP})
developed a set of pre-processing pipelines to process structural,
functional and diffusion MRI data acquired in the project. We focus on HCP
pre-processing pipelines for structural data, in particular PreFreesurfer
and Freesurfer. A detailed description of the analyses done in the
pipelines is available in~\cite{glasser2013minimal}.
% IF NEEDED, ADD MORE DETAILS ABOUT WHAT THE PIPELINES DO
% The structural pre-processing pipelines consists of PreFreeSurfer, 
% FreeSurfer and PostFreeSurfer. In this paper, 
% we analyzed PreFreeSurfer pipeline which consist of various steps 
% including correction of MR 
% gradient nonlinearity distortions, align the T1w and T2w images using 
% FSL FLIRT, Align native space to MNI template using ACPC and FSL FLIRT, 
% brain extraction usin FSL FLIRT and FNIRT to MNI template, register T2w 
% to T1w using FLIRT's BBR, perform a bias field correction, and register 
% the subject's native structural space to MNI space.

@@

In the previous study~\cite{Scaria2017}, we showed that pre-processing 
pipelines of the Human Connectome Project~\cite{Glasser2013} were 
sensitive to operating system variation so that Figure 
\ref{fig:tissue_class} illustrates the binarized errors after brain 
tissue segmentation process in FreeSurfer. In addition, 
Figure~\ref{fig:fnirt_result} shows the same errors occurred in 
non-linear registration process between CentOS6 and CentOS7 in PreFreeSurfer.

@@

The processes that introduce errors in PreFreeSurfer along with the 
number of occurrences are depicted in Figures~\ref{fig:pfs_table, 
fig:pfs_chart} including linear registration with “\emph{FLIRT}” (in 
ACPC Alignment, BrainExtraction, DistortionCorrection, 
AtlasRegistration), non-linear registration with “\emph{FNIRT}” (in 
BrainExtraction and AltasRegistration), image warping with 
“\emph{new\_invwarp}” (in BrainExtraction and AtlasRegistration).  In 
addition, errors were observed in image mean and standard-deviation 
computations with “\emph{fslstats}” (in BiasFieldCorrection), and in 
masked image extrapolation with “\emph{fslmaths}” (in 
BiasFieldCorrection).  Besides, transformation format conversion with 
“\emph{convertwarp}” (in DistortionCorrection) was able to remove 
errors.

@@

The results still suffer from small perturbations literally because of 
the fact that pipeline are not numerically stable. The preferred 
solution is to detect and fix numerical instability of the pipeline 
instead of masking the problem. These processes need to be reviewed to 
understand and correct the cause of instabilities. }

>>>>

Figure~\ref{fig:overview} shows an overview of our method. For each tested
condition, Condition 1 and Condition 2, the pipeline is containerized with
Docker, and its interface is described with
Boutiques~\cite{glatard2017boutiques}. \reprozip~\cite{Chirigati2016} is
added to Condition 1 for provenance tracking. Our tool starts by
identifying temporary files and ``multi-write" files, i.e., files written
by more than one process (Figure~\ref{fig:overview-capturing}). To do that,
the tool first executes the pipeline in Condition 1, to obtain a process
graph (Figure~\ref{fig:overview-capturing} - (1)) and a list of result files.
The list of processes that create intermediary or multi-write
files is then generated (Figure~\ref{fig:overview-capturing} - (2)). 
Using this list, the tool modifies Docker image in Condition 1 and
exectutes the pipeline again through it, which turns to produce results
including temporary and overwritten files
(Figure~\ref{fig:overview-capturing} - (3,4)). In the second step, the
processes are labeled from the differences found in their outputs in the
two tested conditions (Figure~\ref{fig:overview-labelling}). To this order,
the tool builds docker image for Condition 2 by modifying pipeline
processes (Figure~\ref{fig:overview-labelling} - (1)) that recognised from 
the process graph. Then, the modified docker
image is executed in Condition 2 and each process is labeled right after
the running by comparing checksum of the results obtained in Condition 1
and output files of the process in Condition 2
(Figure~\ref{fig:overview-labelling} - (2)). We then label processes in 2
categories depending whether they
create differences (represented in red) or not (green). 
The tool replaces output file with the same file obtained in Condition 1 
if process creates differences (Figure~~\ref{fig:overview-labelling} - (3)).
Process labelling
is done through hooks which are defined during the docker image modifying
procedure, and incremental updates in Condition 2, until the end of the
pipeline execution.

\begin{figure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \includegraphics[width=1\columnwidth]{images/fig1-a}
    \caption{Identification of temporary and multi-write files.
    (\href{https://docs.google.com/drawings/d/1rsbFwPjNPNMRhXUl4RSK3G0OaiJC7K-buiHN0hPD8eQ/edit?usp=sharing}{Source})}
    \label{fig:overview-capturing}
  \end{subfigure}
   \begin{subfigure}{\columnwidth}
    \centering
     \includegraphics[width=1\columnwidth]{images/fig1-b}
     \caption{Labelling process graphs including intermediary files.
     (\href{https://docs.google.com/drawings/d/1yblYuKWAD18aJe5JxBu2h1EysyoQA3YrsQj-1T3s0l8/edit?usp=sharing}{Source})}
     \label{fig:overview-labelling}
   \end{subfigure}
   \caption{An overview of NURM tool in two steps. First capturing intermediary files (a); then
            labelling process graphs (b).}
   \label{fig:overview}
  \end{figure}

@@

We use \reprozip 
to capture: (1) the set of processes created by the
pipeline, using the \texttt{clone()} or \texttt{fork()} system call, and
(2) the set of files read, written and executed by each process, including
temporary files. \reprozip collects this information through the
\texttt{ptrace()} system call and stores it in a SQLite database.

Our tool reconstructs a process tree starting from the first process
created by the pipeline and traversing processes through \texttt{clone()}
and \texttt{fork()} dependencies. Our tool also creates a process \emph{graph} 
(Figure~\ref{fig:overview-capturing} - (1)) from this tree
by adding edges corresponding to file dependencies between processes. A
file dependency is defined between processes A and B if a file written by A
is read by B. Figure~\ref{fig:simple_script} shows an example of a process
tree and graph constructed from the example pipeline in
Listing~\ref{listing:sample-script}.
\begin{listing}
\begin{minted}[frame=single,
  framesep=3mm,
  linenos=false,
  xleftmargin=0pt,
  tabsize=4]{bash}
#!/bin/bash

@@

@@

The label of processes that read or 
write temporary files is undetermined because these files are deleted during 
the execution. To address this issue, we replace in Condition 1 every process P that 
writes temporary files with a modification of P that first calls P and then
saves all its output files to a read-only directory. This replacement is
done by modifying the PATH environment variable to point to a directory
containing a modified version of the executable called by the process. The
modified executable will run the original executable and then save its
output files (see Listing~\ref{listing:modify-script}). 
This 
solution does not cover the temporary files that are removed by P 
itself, but this is not a problem since these files do not play any role in 
the subsequent steps of the pipeline.

\begin{listing}
  \begin{minted}[frame=single,
    framesep=3mm,
    linenos=false,
    xleftmargin=0pt,
    tabsize=4]{python}
  #!/usr/bin/env python
  import os.path as op
  import shutil

  # Run the original executable using the same arguments
  executed_file = sys.argv[0]
  exec_argv = op.join('original_scripts', executed_file)
  exec_argv = exec_argv + " ".join(sys.argv[1:])
  subprocess.Popen(exec_argv, shell=True).communicate()

  # Load list of captured process to be checked
  with open('path/to/p_list/', 'r') as p_list:
      process_list = json.load(p_list)

  if exec_argv in process_list.keys():
      # Save output files to read-only directory
      p_files = process_list[exec_argv]
      shutil.copy(p_files, '/read-only/dir')

  \end{minted}
    \caption{Modified version of the script in Listing~\ref{listing:sample-script} to save intermediary files.}
    \label{listing:modify-script}
  \end{listing}

\subsubsection{Capturing multi-write files}

@@

As an example of this capturing process, in the sample pipeline in 
Listing~\ref{listing:sample-script}, process \texttt{2\#bet2} writes a temporary file and 
also file \emph{T1w\_brain\_bin.nii.gz} is first written by process \texttt{2\#bet2} and 
then overwritten by process \texttt{3\#fslmaths}. The list of these processes is captured in 
Listing~\ref{listing:json_process}.
Using this list, we modify relevant processes in Condition 1 and then re-execute pipeline 
to save them in a backup folder.
Figure~\ref{fig:overview-capturing} - (4) shows pipeline results including intermediary files 
captured as the outputs in Condition 1.

@@

Since all the result files are captured in Condition 1, the tool 
is ready to label the piepeline processes based on the results in Condition 2.
However, another challenge is to label undetermined processes that read files with 
differences and write files with differences too. In this
situation, it is not possible to determine from the pipeline results 
whether the process created differences or 
was transparent.
To address this issue, we set hooks in the pipeline 
in Condition 2. Hooks are set by replacing the pipeline 
processes with a custom script. This custom script labels each process 
as \emph{transparent} or \emph{create differences} immediately after running 
the original executable. 
The replacement is done through the PATH variable, as before. Moreover, 
this custom script copies the results obtained from the same process in 
Condition 1 to the pipeline output in Condition 2 if 
it is invoked with the arguments of a process that created differences 
(Figure~\ref{fig:overview-labelling} - (3)). 
Differences are identified by comparing checksum of the output files for 
the same process in both conditions (Figure~\ref{fig:overview-labelling} - (2)).
We developed an incremental approach that consists of the following steps:

\begin{enumerate}
  \item Start the pipeline execution in Condition 2; 
        after hooking all the processes involved in the pipeline.
  \item Label each process as \emph{transparent} or \emph{create differences} 
        right after its running.
  \item Check if process is \emph{create differences} then: 
        copy the results produced by the same process in Condition 1 to the 
        pipeline output in Condition 2. 
  \item Continue steps 2 and 3 until the end of the pipeline execution.
\end{enumerate}

This algorithm creates a \emph{labeled process tree} at the end of pipeline execution 
which highlights processes that create differences.
(Figure~\ref{fig:overview-labelling} - (4)).

@@

Figure~\ref{fig:iterations} illustrates our incremental labelling 
process for the example in Figure~\ref{fig:simple_script}. At every 
step, processes that created differences are shown in red and other processes 
(transparent processes) are in green. As in 
Figure~\ref{fig:simple_script}, plain black edges represent the process 
tree and dashed edges represent file dependencies: green edges 
represent files with no differences, while red edges represent files with 
differences. Temporary files are not represented because they have been 
saved as previously described.

The four steps in Figure~\ref{fig:iterations} correspond to the 
steps of the labelling algorithm. 
At step one, process \texttt{1\#bet} is executed and then labeled 
as transparent (green) as it produced files without differences.
At step 2, \texttt{2\#bet2} 
is labeled as difference creator (red) as it produced files with differences 
from files without differences. Therefore, the files produced by \texttt{2\#bet2} in  
Condition 2 are replaced with the files produced by \texttt{2\#bet2} in 
Condition 1.
At step 3, after running process \texttt{3\#fslstats}, it labeled as 
transparent as it write files without differences.
At step 4, process \texttt{4\#fslmaths} is labeled as difference creator 
as the last process of the pipeline.
As a result of these 4 steps, the final process labelling is: 
\texttt{2\#bet2} and \texttt{4\#fslmath} are difference creators (red) 
and the other processes are transparent.

@@

Different subjects may lead to different process trees, due to
variations that may be coming from differences in data types or
cardinality. For instance, some images may have been acquired multiple
times in some subjects. Some of these differences can be neglected, for
instance when a data decompression step is present at the beginning of the
execution for some subjects only, and other ones cannot, when different
processing paths are used in different subjects.

We cluster subjects into different types to specify how many different 
\emph{labeled process tree} are generated. This implies the effect of different 
subjects on pipeline results. First, we cluster subjects based on their process 
trees that are labeled by the process name. Then, we cluster subjects in each 
category after re-labeling the processes that create differences. In this order, 
the tree edit distance~\cite{zhang1989simple} is used as similarity measure for 
representing the distance between labeled trees. Tree edit distance  is defined  
as the minimum number of edit operations which is needed to transform one tree into 
the other. Three edit operations are considered: node label modification, 
node removal, and node insertion. Each operation has an associated cost of 1.
With this distance, we cluster subjects using agglomerative hierarchical
clustering as implemented in SciPy~\cite{oliphant2007scipy}
(Algorithm~\ref{algo:hclustering}). As a result, the distance between
any two subjects in a cluster is lower than a threshold parameter.

@@

@@

The Human Connectome Project (\href{https://www.humanconnectome.org}{HCP})
developed a set of pre-processing pipelines to process structural,
functional and diffusion MRI data acquired in the project. We focus on HCP
pre-processing pipelines for structural data, in particular PreFreesurfer
and Freesurfer. A detailed description of the analyses done in the
pipelines is available in~\cite{glasser2013}.
% IF NEEDED, ADD MORE DETAILS ABOUT WHAT THE PIPELINES DO
% The structural pre-processing pipelines consists of PreFreeSurfer, 
% FreeSurfer and PostFreeSurfer. In this paper, 
% we analyzed PreFreeSurfer pipeline which consist of various steps 
% including correction of MR 
% gradient nonlinearity distortions, align the T1w and T2w images using 
% FSL FLIRT, Align native space to MNI template using ACPC and FSL FLIRT, 
% brain extraction usin FSL FLIRT and FNIRT to MNI template, register T2w 
% to T1w using FLIRT's BBR, perform a bias field correction, and register 
% the subject's native structural space to MNI space.

@@

In the previous study~\cite{Scaria2017}, we showed that pre-processing 
pipelines of the Human Connectome Project~\cite{glasser2013} were 
sensitive to operating system variation so that Figure 
\ref{fig:tissue_class} illustrates the binarized errors after brain 
tissue segmentation process in FreeSurfer. In addition, 
Figure~\ref{fig:fnirt_result} shows the same errors occurred in 
non-linear registration process between CentOS6 and CentOS7 in PreFreeSurfer.

@@

The processes that introduce errors in PreFreeSurfer along with the 
number of occurrences are depicted in Figures~\ref{fig:pfs_table} and 
~\ref{fig:pfs_chart} including linear registration with “\emph{FLIRT}” (in 
ACPC Alignment, BrainExtraction, DistortionCorrection, 
AtlasRegistration), non-linear registration with “\emph{FNIRT}” (in 
BrainExtraction and AltasRegistration), image warping with 
“\emph{new\_invwarp}” (in BrainExtraction and AtlasRegistration).  In 
addition, errors were observed in image mean and standard-deviation 
computations with “\emph{fslstats}” (in BiasFieldCorrection), and in 
masked image extrapolation with “\emph{fslmaths}” (in 
BiasFieldCorrection).  Besides, transformation format conversion with 
“\emph{convertwarp}” (in DistortionCorrection) was able to remove 
errors.

@@

The results still suffer from small perturbations literally because of 
the fact that pipeline are not numerically stable. The preferred 
solution is to detect and fix numerical instability of the pipeline 
instead of masking the problem. These processes need to be reviewed to 
understand and correct the cause of instabilities.

It should be noted that processes that remove differrences, read files with differences and 
write files without differences, are not recognised 
by this method.
}
